Lawrence Bull, PhD

### 2024-12-17 index.qmd
bio update

Research Fellow [[Stats, UoG]](https://www.gla.ac.uk/schools/mathematicsstatistics/staff/lawrencebull/#biography) in machine learning for physical systems. Particularly tools to encode structure (via domain knowledge) into data-driven models. Statistical methods for telemetry data from machines and infrastructure.

Applications have included [planes](https://www.sciencedirect.com/science/article/pii/S0022460X21001449), [trains](https://arxiv.org/abs/2403.17820), [automobiles](https://doi.org/10.48550/arXiv.2204.12404) (.. [wind turbines](https://arxiv.org/abs/2111.15496)).
By encoding domain expertise into statistical models, complex representations can be built from interpretable units, allowing machines to share information and increasing the value of data.

>>>>

Research Fellow in machine learning for physical systems. Particularly tools to encode structure (via domain knowledge) into data-driven models. Mostly to monitor and simulate machines/infrastructure, by utilising telemetry data.

Applications have included [planes](https://www.sciencedirect.com/science/article/pii/S0022460X21001449), [trains](https://arxiv.org/abs/2403.17820), [automobiles](https://doi.org/10.48550/arXiv.2204.12404) (.. [wind turbines](https://arxiv.org/abs/2111.15496)).
By encoding domain expertise into statistical models, complex representations can be built from interpretable units, increasing the value of sensing and fusing physics with data.
